Multidimensional signals and analytic flexibility: Estimating degrees of freedom in human speech analyses

### 2023-01-27 RR_manuscript/RR.Rmd

The results section is divided into three parts.
We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings.
Second, we report the results of the meta-analytic model, focusing on between-team and between-model variability. 
<!-- and the estimated meta-analytic effect of word combination typicality on speech acoustics.-->
Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
The research compendium of the study, containing all the code and data presented here, can be found in the GitHub repository linked in the research compendium at <https://osf.io/3bmcp/>, in the `scripts/r/` folder.

@@

Our quantitative assessment did not include other degrees of freedom, all of which are additional sources of variation: 
Teams differed with regard to how the acoustic signal was segmented ranging from fully automated forced-alignment with minimal manual correction to complete manual alignment performed by the analysts; teams differed in whether the statistical analysis was based on a subset of the data or the whole dataset; and they differed whether and if so how measurements were excluded based on both qualitative (i.e. whether specific speech production instances were excluded or not) and quantitative grounds (i.e. whether data were trimmed or not).

>>>>

The results section is divided into three parts.
We first provide a statistical description of team composition, nature of acoustic analyses and statistical approaches, and peer-review ratings.
Second, we report the results of the meta-analytic model, focusing on between-team and between-model variability. 
<!-- and the estimated meta-analytic effect of word combination typicality on speech acoustics.-->
Finally, we present the analysis of the effect of analytic and researcher-related predictors on the meta-analytic effect.
The research compendium of the study, containing all the code and data presented here, can be found in the GitHub repository linked in the research compendium at <https://osf.io/3bmcp/>, in the `scripts/r/` folder.
An interactive web application that allows the interested reader to explore the data set is available at <https://many-speech-analyses.github.io/shiny>.

@@

Our quantitative assessment did not include other degrees of freedom, all of which are additional sources of variation: 
Teams differed with regard to how the acoustic signal was segmented ranging from fully automated forced-alignment with minimal manual correction to complete manual alignment performed by the analysts; teams differed in whether the statistical analysis was based on a subset of the data or the whole data set; and they differed whether and if so how measurements were excluded based on both qualitative (i.e. whether specific speech production instances were excluded or not) and quantitative grounds (i.e. whether data were trimmed or not).
